HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
iaa disagree

\XXX{Discussion of the disagreements}

\begin{compactitem}
  \item German has low overall proportion of orange annotation (1.2\% compared with 4.5-8.6)
  \item German annotators give a lot of green (so skewed classes, high expected agreement), but 
        differ more significantly on what should be green. 
  \item For Polish, big difference in number of As (2000 vs 1500) given by each annotator
  \item For Czech structural, both annotators give higher proportion of As, raising the expected agreement.
\end{compactitem}

>>>>

Looking more closely at the areas of disagreement, we see that for the Polish structural nodes, the 
proportion of As was quite different between the two annotators (53\% vs. 71\%), whereas for other
languages the annotators agree in the proportions. We believe that this was because one of the Polish
annotators did not fully understand the guidelines for structural nodes, and percolated
errors up the tree, creating more Bs. For the German lexical nodes, and Czech structural nodes, where
Kappa is also around 0.3, the proportion of such nodes being marked as ``correct'' is relatively 
high, meaning that the class distribution is more skewed, so the expected agreement used in the
Kappa calculation is high, lowering Kappa. Essentially, the annotation problem is harder when the classes
are more skewed. Finally we note some evidence of domain-specific disagreements, for instance the German
MT system normally translated ``review'' (as in ``systematic review'' -- a frequent term in the 
Cochrane texts) as ``\"uberpr\"ufung'', which 
one annotator marked correct, and the other (a Cochrane employee)  as incorrect.
